---
title: "Meta-Analysis of Digital Neuropsychological Interventions"
knit: (function(input, ...) { out_dir <- file.path(dirname(input), "reports"); if (!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE); outs <- rmarkdown::render(input, output_format = "all"); file.copy(outs, out_dir, overwrite = TRUE); file.remove(outs); invisible(out_dir) })
output:
  html_document:
    toc: true
    fig_width: 10
    fig_height: 6
    fig_caption: true
  word_document:
    toc: true
    fig_width: 10
    fig_height: 6
    fig_caption: true
    reference_docx: assets/template.docx
  pdf_document:
    latex_engine: xelatex
    toc: true
editor_options:
  chunk_output_type: inline
  markdown:
    wrap: sentence
mainfont: Helvetica Neue
zotero: true
bibliography:
  - assets/references.yaml
  - assets/grateful-refs.bib
---

# 1. Introduction

This R Markdown report contains the entire script used for the meta-analysis on digital neuropsychological interventions for patients with alcohol use disorder.

It is build as an R Environment (`renv`) for managing R package versions and maximizing the reproducibility for future analyses, and all package versions are stored in the renv.lock-file.

The packages needed for this report are `rmarkdown`, `knitr`, `here`, `osfr`, `devtools`, `robvis`, `readxl`, `openxlsx`, `dplyr`, `tidyr`, `tidyverse`, `meta`, `ggplot2`, `grid`, `gtable`, `cowplot`, and `grateful`.
The `rmarkdown` and `knitr` packages are used for knitting the R markdown file to PDF or word, the `here` package is used to build file paths relative to the project root (so the report works regardless of the working directory), and `osfr` is used to retrieve the project data from the OSF repository.
The `devtools` package is used to install the developer version of `robvis`, which is required as this version displays the study labels horizontally; `robvis` itself is used to create the traffic light plot and the summary of the risk of bias ratings.
The `readxl` and `openxlsx` packages are used for reading and writing the Excel data sets, whereas the `dplyr`, `tidyr`, and `tidyverse` packages are used for transforming and preparing the data for the analyses.
All the effect sizes are calculated using the `meta` package, and forest and funnel plots are generated using this package as well.
The `ggplot2`, `grid`, and `gtable` packages are used to build and fine-tune the plots (for example, adding statistics and frame lines that are not standard for the `meta` or `robvis` packages), and the `cowplot` package is used to combine the individual funnel plots into a single figure.
Finally, to document all the packages used and the corresponding versions, we used the `grateful` package to create a summary and a list of references for each of the used packages in this analysis report.

The full R analysis environment, including all scripts and supporting files, is available in the following public GitHub repository: <https://github.com/mrst3rz/digital-npi-for-aud>

## 1.1 Loading and installing the packages

To prepare the R environment for the analyses, we first need to install the required packages.

```{r package-setup, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE, cache=FALSE}
# List of required CRAN packages
packages_required <- c("osfr", "rmarkdown", "knitr", "here", "readxl", "openxlsx", "dplyr",
                        "meta", "grid", "gtable", "devtools", "tidyr", "tidyverse", "ggplot2",
                        "grateful", "cowplot")

# Function to install missing CRAN packages
install_if_missing <- function(pkg) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg)
  }
}

# Install all missing CRAN packages
invisible(sapply(packages_required, install_if_missing))

# Load all the packages
invisible(lapply(packages_required, library, character.only = TRUE))

# Install robvis dev version from GitHub to display study labels horizontally
# The CRAN version does not support horizontal labels, so we check for the dev version specifically
if (!requireNamespace("robvis", quietly = TRUE) ||
    packageVersion("robvis") >= "0.3.1") {
  devtools::install_github("mcguinlu/robvis", force = TRUE)
}

# Load latest robvis-version
library(robvis)
```

A snapshot of the R environment can be performed, after the packages have been installed by running renv::snapshot.

```{r snapshot-renv, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Snapshot the environment
renv::snapshot(prompt = FALSE)
```

```{r knitr-setup, message=FALSE, warning=FALSE, include=FALSE}
# Set the global knitr-settings for the present R markdown document.
# cache = TRUE stores each chunk's results so that re-rendering only re-runs
# chunks that have changed; autodep tracks dependencies between chunks. The
# package-setup chunk runs before this one and is set cache = FALSE, so the
# libraries are always attached on every render.
#
# cache.path is made FORMAT-SPECIFIC (cache/latex/, cache/html4/, cache/docx/,
# ...). Knitting to multiple formats (output_format = "all") re-runs the whole
# document once per format, and each format saves its figures to a different
# folder (figure-html/, figure-docx/, figure-latex/). If all formats shared one
# cache, a chunk could be skipped as a "cache hit" for e.g. the PDF pass simply
# because it already ran for HTML - but its PDF-specific figure file would then
# never be created, leaving pandoc unable to find it ("Could not fetch
# resource ... figure-latex/...: replacing image with description"). A
# separate cache directory per format means every format always regenerates
# its own figures on first render, while still caching normally within that
# format on subsequent re-renders.
pandoc_to <- knitr::opts_knit$get("rmarkdown.pandoc.to")
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	cache = TRUE,
	autodep = TRUE,
	cache.path = paste0("cache/", if (is.null(pandoc_to)) "default" else pandoc_to, "/")
)
```

```{r osf-auth-setup, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Load the OSF token
osf_auth()
```

First we load the project data from the online repository OSF, which is done with the package `osfr`.
This can be skipped, if the data has already been stored locally.
A token for accessing the project data is needed during the embargo period.

```{r osf-proj-load, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Local directory for storing the downloaded data, anchored to the project root
# with here() so the path resolves whether the main file is knitted or a child
# file is run on its own. Keeping the data on disk means it is only fetched from
# OSF once, which greatly speeds up re-rendering.
data_dir <- here::here("data")
if (!dir.exists(data_dir)) dir.create(data_dir)

# Directories for the generated outputs (created up front so the figure and data
# exports later in the report always have somewhere to write to)
dir.create(here::here("outputs", "figures"), showWarnings = FALSE, recursive = TRUE)
dir.create(here::here("outputs", "data"),    showWarnings = FALSE, recursive = TRUE)
dir.create(here::here("assets"),             showWarnings = FALSE, recursive = TRUE)
dir.create(here::here("reports"),            showWarnings = FALSE, recursive = TRUE)

# Expected local file paths for the two data sets
rob_local      <- file.path(data_dir, "Risk of Bias Data.csv")
clinical_local <- file.path(data_dir, "Extracted Clinical Outcome Data.xlsx")

# Only contact OSF if the data has not already been stored locally
if (!file.exists(rob_local) || !file.exists(clinical_local)) {

  # Get the OSF project node
  osf_proj <- osf_retrieve_node("9xtsq")

  # List all folders inside the project
  osf_folders <- osf_ls_files(osf_proj, type = "folder")

  # Retrieve the "Risk of bias data" and "Clinical outcome data" folders
  osf_rob_folder <- osf_retrieve_file(
    osf_folders %>% filter(name == "Risk of bias data") %>% pull(id))
  osf_clinical_folder <- osf_retrieve_file(
    osf_folders %>% filter(name == "Clinical outcome data") %>% pull(id))

  # Download the desired files into the local data directory
  osf_ls_files(osf_rob_folder) %>%
    filter(name == "Risk of Bias Data.csv") %>%
    osf_download(path = data_dir, conflicts = "overwrite")

  osf_ls_files(osf_clinical_folder) %>%
    filter(name == "Extracted Clinical Outcome Data.xlsx") %>%
    osf_download(path = data_dir, conflicts = "overwrite")
}

# Expose the local paths through the same interface the rest of the report uses,
# so no downstream code needs to change
osf_rob_files      <- list(local_path = rob_local)
osf_clinical_files <- list(local_path = clinical_local)
```

```{r child-risk-of-bias, child = "children/01-risk-of-bias.Rmd"}
```

```{r child-short-term, child = "children/02-short-term.Rmd"}
```

```{r child-intermediate, child = "children/03-intermediate-term.Rmd"}
```

```{r child-long-term, child = "children/04-long-term.Rmd"}
```

```{r child-exploratory, child = "children/05-exploratory.Rmd"}
```

```{r child-exports, child = "children/06-exports.Rmd"}
```

# 7. R packages used

Some of the auxiliary packages used in this analysis report can be outputted using the package `grateful` by @rodriguez-sanchezaut2025.
The version number and the corresponding reference of the package are listed next to the package name in the package below.

```{r packages-overview, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Inline summary table of the packages used. This also writes the
# grateful-refs.bib bibliography (into assets/) that the report cites from.
cite_packages(output = "table", out.dir = here::here("assets"))

# Standalone grateful report (package citations) saved to reports/
cite_packages(output = "file", out.format = "docx", out.dir = here::here("reports"))
```

\newpage

# 8. References
