## 1.3 Importing risk of bias data

Before conducting the meta-analyses, we want to create two plots for the risk of bias (RoB) assessments for the included studies.
We used the revised version of the risk of bias tool (RoB 2), and the plots adhere to the domains specified by @sterne2019.

The first step to display the risk of bias results, requires that a separate data set is imported, and as this file is formatted as a csv-file, we can use the readr-package.

```{r import-rob, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Importing csv-file containing the RoB data set
rob_d <- read.csv(osf_rob_files$local_path, sep = ",", header = TRUE)
```

## 1.4 Displaying the risk of bias

After the data set has been imported, we can create the traffic light plot using the function called rob_traffic_light(), which will display the individual ratings for each domain for each of the included studies.

```{r traffic-plot, echo=TRUE, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Traffic plot of individual risk of bias ratings"}
# Create a traffic plot displaying individual bias ratings
traffic_plot <- rob_traffic_light(rob_d, tool = "ROB2", psize = 7)

# Remove alternating grey row stripes
traffic_plot$layers[[4]]$aes_params$fill <- "#ffffff"
traffic_plot$layers[[4]]$aes_params$colour <- "#ffffff"

# Slight nudge right for symbols (+, -, X) to centre within circles
traffic_plot$layers[[2]]$position <- position_nudge(x = 0.0075)
traffic_plot$layers[[7]]$position <- position_nudge(x = 0.0072, y = 0.01)

# position_nudge only affects the plot, not the legend key, so override the
# key drawing for the symbol layer to shift the symbol right to match the peas
traffic_plot$layers[[2]]$geom <- ggproto("GeomPointNudge", GeomPoint,
  draw_key = function(data, params, size) {
    key <- draw_key_point(data, params, size)
    key$x <- key$x + unit(0.4, "pt")
    key
  })

# Restore black circle outline on the peas in the plot
traffic_plot$layers[[6]]$aes_params$colour <- "black"

# The legend key is built from layer 1 (the disc). Give it a fill-mapped,
# black-ringed shape 21 so the key shows a colored pea WITH a black outline.
# In the plot this layer sits under the larger size-7 disc (layer 5), so this
# affects only the legend key, not the plotted peas.
traffic_plot$layers[[1]]$mapping           <- aes(fill = judgement)
traffic_plot$layers[[1]]$aes_params$shape  <- 21
traffic_plot$layers[[1]]$aes_params$colour <- "black"
traffic_plot$layers[[1]]$aes_params$stroke <- 0.5

# Rename Overall to O in all data sources
traffic_plot$data$domain[traffic_plot$data$domain == "Overall"] <- "OA"
for (i in seq_along(traffic_plot$layers)) {
  d <- traffic_plot$layers[[i]]$data
  if (!is.null(d) && nrow(d) > 0 && "domain" %in% names(d)) {
    traffic_plot$layers[[i]]$data$domain[d$domain == "Overall"] <- "OA"
  }
}
rm(i, d)  # drop loop temporaries so they don't linger in the environment
traffic_plot <- traffic_plot +
  facet_grid(Study ~ factor(domain, levels = c("D1", "D2", "D3", "D4", "D5", "OA")),
             switch = "y", space = "free")

# Linewidth for plot lines, and a thinner one for the judgement box
legend_lw <- 0.4
legend_box_lw <- 0.25

# Build the styled plot
traffic_plot <- traffic_plot +
  scale_y_continuous(limits = c(0.5, 1.5), labels = NULL, breaks = NULL,
                     name = NULL, position = "left",
                     # Symmetric expansion centres each pea in its cell so the top
                     # row does not touch the header line (row spacing is unchanged)
                     expand = expansion(add = c(0.15, 0.15))) +
  scale_x_discrete(position = "top", name = NULL) +
  labs(caption = NULL) +
  scale_colour_manual(
    values = c(h = "#BF0000", s = "#E2DF07", l = "#02C100",
               n = "#4EA1F7", x = "#cccccc"),
    breaks = c("h", "s", "l"),
    labels = c("High risk", "Some concerns", "Low risk"),
    name = "Judgement"
  ) +
  scale_shape_manual(
    values = c(l = 43, s = 45, h = 120, n = 63, x = 32),
    breaks = c("h", "s", "l"),
    labels = c("High risk", "Some concerns", "Low risk"),
    name = "Judgement"
  ) +
  # Fill scale drives the coloured disc in the legend key (see layer 1 above)
  scale_fill_manual(
    values = c(h = "#BF0000", s = "#E2DF07", l = "#02C100",
               n = "#4EA1F7", x = "#cccccc"),
    breaks = c("h", "s", "l"),
    labels = c("High risk", "Some concerns", "Low risk"),
    name = "Judgement"
  ) +
  guides(
    # Hide the raw colour legend; the fill guide draws the ringed coloured pea
    # and the shape guide overlays the +/-/x symbol on top of it.
    colour = "none",
    fill  = guide_legend(override.aes = list(size = 7),   direction = "vertical"),
    shape = guide_legend(override.aes = list(size = 4.5), direction = "vertical")
  ) +
  theme(
    strip.background.y = element_rect(fill = "white", colour = NA),
    strip.background.x = element_rect(fill = "white", colour = NA),
    strip.text.x = element_text(face = "bold", size = 10,
                                 margin = margin(t = 2, b = 12, l = 0, r = 0)),
    strip.text.y.left = element_text(angle = 0, size = 10, hjust = 0),
    panel.border = element_blank(),
    panel.spacing.x = unit(-3, "pt"),
    panel.spacing.y = unit(0, "pt"),
    legend.position = "bottom",
    legend.direction = "vertical",
    legend.justification = "right",
    legend.margin = margin(t = 4, r = 6, b = 6, l = 6),
    legend.box.margin = margin(t = 14, r = 0, b = 4, l = 0),
    legend.background = element_rect(fill = "white", colour = "black",
                                      linetype = "solid", linewidth = legend_box_lw),
    legend.key = element_rect(fill = "white"),
    legend.key.size = unit(1.0, "lines"),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 10, face = "plain")
  )

# Add header line, bottom line, and vertical separator via gtable.
# Building the plot here is where ggplot2 raises a few advisory warnings
# ("Duplicated override.aes", "All aesthetics have length 1...") caused by the
# layer surgery above (re-mapping layer 1 to draw the ringed legend key). The
# resulting plot is visually correct (verified), so these are expected and
# suppressed at their source rather than hidden with a blanket chunk option.
traffic_gt <- suppressWarnings(ggplot_gtable(ggplot_build(traffic_plot)))

panel_layout <- traffic_gt$layout[grepl("^panel-", traffic_gt$layout$name), ]
strip_l <- traffic_gt$layout[grepl("^strip-l", traffic_gt$layout$name), ]
strip_t <- traffic_gt$layout[grepl("^strip-t", traffic_gt$layout$name), ]

top_row <- min(strip_t$t)
header_bottom <- max(strip_t$b)
bottom_row <- max(panel_layout$b)
left_col <- min(strip_l$l)
right_col <- max(panel_layout$r)
sep_col <- min(panel_layout$l)

# Match legend box line thickness (convert ggplot2 mm to grid pt)
line_col <- "black"
line_lwd <- legend_box_lw * ggplot2::.pt

# Nudge the horizontal frame lines away from the peas by a fixed amount
gap_top <- unit(5, "pt")   # header line raised (also moves it toward the labels)
gap_bot <- unit(8, "pt")   # bottom line lowered (away from the last pea row)

# Header bottom line
traffic_gt <- gtable::gtable_add_grob(traffic_gt,
  grid::segmentsGrob(x0 = 0, x1 = 1, y0 = gap_top, y1 = gap_top,
    gp = grid::gpar(col = line_col, lwd = line_lwd)),
  t = header_bottom, b = header_bottom, l = left_col, r = right_col,
  clip = "off", name = "header-bottom")

# Bottom line below last study
traffic_gt <- gtable::gtable_add_grob(traffic_gt,
  grid::segmentsGrob(x0 = 0, x1 = 1,
    y0 = unit(0, "npc") - gap_bot, y1 = unit(0, "npc") - gap_bot,
    gp = grid::gpar(col = line_col, lwd = line_lwd)),
  t = bottom_row, b = bottom_row, l = left_col, r = right_col,
  clip = "off", name = "bottom-line")

# Vertical separator between study labels and D1 (extended down to meet bottom line)
traffic_gt <- gtable::gtable_add_grob(traffic_gt,
  grid::segmentsGrob(x0 = 0, x1 = 0, y0 = unit(0, "npc") - gap_bot, y1 = 1,
    gp = grid::gpar(col = line_col, lwd = line_lwd)),
  t = top_row, b = bottom_row, l = sep_col, r = sep_col,
  clip = "off", name = "vert-separator")

grid::grid.newpage()
grid::grid.draw(traffic_gt)
```

To display the summary of risk of bias across the domains including the overall risk of bias, we can create a new bar plot using the rob_summary() function.
To begin with we set the weighted parameter to FALSE, as we will calculate the weights at the end of the report.

```{r rob-summary, fig.height=5, fig.width=10, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Summary of risk of bias ratings"}
# Create a summary (bar plot) of risk of bias assessments
rob_summary_plot <- rob_summary(rob_d, tool = "ROB2", weighted = FALSE)

# Replace full domain names with D1–D5 and O
levels(rob_summary_plot$data$domain) <- c(
  "Weights"                                            = "Weights",
  "Overall risk of bias"                               = "OA",
  "Bias in selection of the reported result"           = "D5",
  "Bias in measurement of the outcome"                 = "D4",
  "Bias due to missing outcome data"                   = "D3",
  "Bias due to deviations from intended interventions" = "D2",
  "Bias arising from the randomization process"        = "D1",
  "Study"                                              = "Study"
)

# Custom styling
rob_sum_styled <- rob_summary_plot +
  theme(
    axis.text.y    = element_text(face = "bold", size = 13, margin = margin(r = 10)),
    axis.text.x    = element_text(size = 13),
    axis.line.y    = element_line(colour = "black", linewidth = 0.4),
    legend.text    = element_text(size = 12),
    legend.title   = element_text(size = 12),
    legend.position    = "bottom",
    legend.direction   = "horizontal",
    legend.justification = "center",
    legend.background  = element_rect(fill = "white", colour = "black",
                                      linetype = "solid", linewidth = 0.4),
    legend.margin      = margin(6, 6, 6, 6),
    legend.box.margin  = margin(5, 0, 5, 0)
  ) +
  # reverse = TRUE: Low risk first, High risk last; weighted bar plot will be created later
  guides(fill = guide_legend(title = NULL, nrow = 1, reverse = TRUE))

# Stretch the legend box to span the full figure width via gtable
rob_sum_gt <- ggplotGrob(rob_sum_styled)

leg_nms <- intersect(
  rob_sum_gt$layout$name,
  c("guide-box", "guide-box-bottom", "guide-box-top",
    "guide-box-left", "guide-box-right", "guide-box-inside")
)

# Span full figure width (column 1 to last column)
l_col <- 1L
r_col <- ncol(rob_sum_gt)

for (nm in leg_nms) {
  idx   <- which(rob_sum_gt$layout$name == nm)
  t_row <- rob_sum_gt$layout$t[idx]
  b_row <- rob_sum_gt$layout$b[idx]

  rob_sum_gt$layout$l[idx] <- l_col
  rob_sum_gt$layout$r[idx] <- r_col

  # Full-width background rectangle drawn behind the legend content
  rob_sum_gt <- gtable::gtable_add_grob(
    rob_sum_gt,
    grid::rectGrob(gp = grid::gpar(fill = "white", col = "black",
                                   lwd = 0.4 * ggplot2::.pt)),
    t = t_row, b = b_row, l = l_col, r = r_col,
    name = "legend-bg-full", z = min(rob_sum_gt$layout$z) - 1
  )
}
# Display the plot
grid.newpage()
grid.draw(rob_sum_gt)
```
