# 3. Main analyses on intermediate-term outcomes

The second part of the main analyses will be conducted on the intermediate time points.
Intermediate effects will consist of studies examining intervention effects six months after discharge.
We still use the excel-dataset "Extracted Clinical Outcome Data", but this time we will only be filtering the data sheets by time point for the calculation of effect sizes and not when conducting the meta-analyses

## 3.1 Intermediate-term abstinence

The first part be conducted on our primary outcome of abstinence, and we calculate the effect sizes for the intermediate-term time point.

### 3.1.1 Calculation of effect sizes for intermediate categorical variables

We want to follow the procedure of converting the continuous variables to categorical outcomes and in opposite direction as mentioned previously and to begin with we only do this for the intermediate time point.

```{r abs-6m-filter, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Filter 6 month data first and store it as a new subset
abs_d_6m <- abs_d %>% filter(time_point == "6 months")
```

The calculation of effect sizes will be done by the inbuilt functions in the meta-package, so for the categorical variables, we will use the metabin() function.

```{r abs-6m-metabin, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Calculating the lnORs using metabin()
abs_metabin_6m <- metabin(
  event.e = e_abs,
  n.e = e_n,
  event.c = c_abs,
  n.c = c_n,
  studlab = study,
  data = abs_d_6m,
  sm = "OR",
  method.tau = "REML",
  method.random.ci = "classic",
  random = TRUE,
  incr = 0.5,
  allstudies = TRUE
)
```

After we have calculated the lnORs, we can create a new data frame and store these values alongside with the other relevant variables (e.g., time point, number of abstinents, etc.) from our original dataset.
As performed previously, we calculate the ORs and SMDs using the Chinn-factor.
Finally, we add the z- and p-values to the data-frame.

```{r abs-6m-combined-data, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Fetching the previously stored data frame and adding the lnORs, their SE and 95% CI
abs_d_full_6m <- data.frame(
  row_id = abs_d_6m$row_id,
  study = abs_metabin_6m$studlab,
  time_point = abs_d_6m$time_point,
  system = abs_d_6m$system,
  intervention = abs_d_6m$intervention,
  total_n = abs_d_6m$e_n + abs_d_6m$c_n,
  c_n = abs_d_6m$c_n,
  c_abs = abs_d_6m$c_abs,
  c_non_abs = abs_d_6m$c_n - abs_d_6m$c_abs,
  e_n = abs_d_6m$e_n,
  e_abs = abs_d_6m$e_abs,
  e_non_abs = abs_d_6m$e_n - abs_d_6m$e_abs,
# Extracting the lnORs from the metabin results
  lnOR = abs_metabin_6m$TE,
  SElnOR = abs_metabin_6m$seTE,
  lnLCI = abs_metabin_6m$lower,
  lnUCI = abs_metabin_6m$upper,
# Calculating the ORs from the metabin results
  OR = exp(abs_metabin_6m$TE),
  OrSE = exp(abs_metabin_6m$TE) * abs_metabin_6m$seTE,
  OrLCI = exp(abs_metabin_6m$lower),
  OrUCI = exp(abs_metabin_6m$upper),
# Caculating the SMD, SE and 95% CI using the Chinn-function
  SMD = abs_metabin_6m$TE * chinn_lnor_to_smd,
  SE = abs_metabin_6m$seTE * chinn_lnor_to_smd,
  LCI = abs_metabin_6m$lower * chinn_lnor_to_smd,
  UCI = abs_metabin_6m$upper * chinn_lnor_to_smd,
# Adding the z- and p-values
  `z-value` = abs_metabin_6m$TE / abs_metabin_6m$seTE,
  `p-value` = 2 * (1 - pnorm(abs(abs_metabin_6m$TE / abs_metabin_6m$seTE))),
# Adding a final note on how data was converted    
  Notes = "Continuous variables converted from categorical outcome (metabin) using Chinn's formula",
  check.names = FALSE
)
```

We want to have the APA author labels rather than study IDs.

```{r abs-6m-assign-labels}
# Assign the new study labels to the combined data frame
abs_d_full_6m$study <- ifelse(abs_d_full_6m$study %in% names(study_labels),
                            study_labels[abs_d_full_6m$study],
                            abs_d_full_6m$study)
```

We want to have the author labels sorted alphabetically rather than in accordance with the pre-specified study IDs and row numbers, so we first arrange the list of studies.

```{r abs-6m-arrange-alpha, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Arrange studies alphabetically
abs_d_full_6m <- abs_d_full_6m %>%
  arrange(study)
```

To make it clearer in the final forest plot, we assign new variable names to the two subgroups, and sort them with the subgroup with the lowest number of studies on top.

```{r abs-6m-rename-subgroups, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Assigning new variable names to the subgroups
abs_d_full_6m <- abs_d_full_6m %>%
  dplyr::rename(`Cognitive system` = system) %>%
  dplyr::mutate( # Changing the order of the two subgroups
    `Cognitive system` = factor(`Cognitive system`,
                      levels = c("Implicit", "Explicit"))
    )
```

With the new subgroup names, we can pool the effects across studies and stratify by the cognitive systems targeted by the intervention used in each study.
This is achieved by using metagen(), where we define our treatment effect (TE) as the lnOR and corresponding standard error of the treatment effect (seTE) as the SE of the lnOR.
We apply a random effects model using REML and use a classic *z*-test.

```{r abs-6m-metagen, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Run the meta-analysis stratified by cognitive systems and using the new labels
abs_metagen_6m <- metagen(TE = lnOR,
                    seTE = SElnOR,
                    studlab = study,
                    data = abs_d_full_6m,
                    subgroup = `Cognitive system`,
                    sm = "OR",
                    method.tau = "REML",
                    common = FALSE,
                    random = TRUE,
                    method.random.ci = "classic")

# Print the results of the meta-analysis
print(abs_metagen_6m)
```

We can now calculate the baseline control risk for the intermediate-term effects by only including studies with categorical outcomes.

```{r abs-6m-ctrl-abs-rate, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Abstinence rate risk difference across all studies on short-term effects
p_c_abs_6m <- with(abs_d_full_6m, sum(c_abs) / sum(c_n))
```

### 3.1.2 Meta-analysis of intermediate-term effects on abstinence

The test statistics for the overall pooled effect size as well as the subgroup effect sizes have now been calculated, but by default, these are not displayed in the forest plot created with the forest()-function in the meta-package.
These values can be displayed, if we first extract the test statistics and store them as separate data-frames.
The data frames can then be added manually to the forest plot with the grid-package.

```{r abs-6m-zp-values, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Extract the test statistics for the overall effect and create a data frame
abs_zp_overall_6m <- data.frame(
  lnOR = abs_metagen_6m$TE.random,
  lnOR_se = abs_metagen_6m$seTE.random,
  NNT = round(nnt(exp(abs_metagen_6m$TE.random), p_c_abs_6m)),
  z_value = abs_metagen_6m$statistic.random,
  p_value = abs_metagen_6m$pval.random
)

# Extract the test statistics for the subgroup analysis and create a data frame
abs_zp_subgroup_6m <- data.frame(
  subgroup = abs_metagen_6m$bylevs,
  lnOR = abs_metagen_6m$TE.random.w,
  lnOR_se = abs_metagen_6m$seTE.random.w,
  NNT = round(nnt(exp(abs_metagen_6m$TE.random.w), p_c_abs_6m)),
  z_value = abs_metagen_6m$statistic.random.w,
  p_value = abs_metagen_6m$pval.random.w
)
```

For an easier way to add the individual effect sizes for each subgroup in the final forest plot, we can create a split of the data frame.

```{r abs-6m-subgroup-split, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Split the previously defined data frame by each cognitive system
abs_zp_subsplit_6m <- split(abs_zp_subgroup_6m, abs_zp_subgroup_6m$subgroup)
```

With the final preparation completed, we can plot the forest plot using the random effects model with the additional test statistics added with the grid-package.
The forest plot uses the BMJ layout (i.e., added weights for the individual studies) and it shows the number of events (i.e., abstinents), the group size for both the intervention (i.e., Intv.) and the control group (i.e., Ctrl), OR effects for individual studies across subgroups as well as the overall effect.
A prediction interval is added to the pooled effect sizes.
For the heterogeneity analyses, we report the Cochran's *Q* statistic, its *p*-value as well as the measure of absolute variance using $I^2$.

```{r abs-6m-forest, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Forest plot for the intermediate-term effects on abstinence"}
# Now plot the forest plot again with new subgroup names
forest(abs_metagen_6m,
       prediction = TRUE,
       prediction.subgroup = FALSE,
       layout = "BMJ",
       subgroup = TRUE,
       overall = TRUE,
       random = TRUE,
       common = FALSE,
       test.subgroup = FALSE,
       print.stat = FALSE,
       print.I2 = TRUE,
       print.Q = TRUE,
       print.pval.Q = TRUE,
       print.tau2 = FALSE,
       label.left = "Favors Control",
       label.right = "Favors Intervention",
       spacing = 1.2,
       fontsize = 10,
       digits = 2,
       xlim = c(1/30, 30),
       at = c(0.03, 0.08, 0.2, 0.5, 1, 2, 5, 12, 30),
       leftcols = c("studlab", "e_abs", "e_n", "c_abs", "c_n"),
       leftlabs = c("Study", "Intv. (events)", "Total (n)", "Ctrl. (events)", "Total (n)"),
  # Right side: default BMJ columns
       rightcols = c("w.random", "effect", "ci"),
       rightlabs = c("Weight (%)", "OR", "95% CI")
       )

# Add a footer for the test statistics of the effects for implicit system
footer_imp_abs_6m <- paste0(
  "Subgroup effect ",
  paste0(
    ": z = ", round(abs_zp_subsplit_6m$Implicit$z_value, 2),
    ", p = ", formatC(abs_zp_subsplit_6m$Implicit$p_value, digits = 2),
    ", NNT = ", abs_zp_subsplit_6m$Implicit$NNT
  )
)

# Add a footer for the test statistics of the effects for explicit system
footer_exp_abs_6m <- paste0(
  "Subgroup effect",
  paste0(
    ": z = ", round(abs_zp_subsplit_6m$Explicit$z_value, 2),
    ", p = ", formatC(abs_zp_subsplit_6m$Explicit$p_value, digits = 2),
    ", NNT = ", abs_zp_subsplit_6m$Explicit$NNT
  )
)

footer_over_abs_6m <- paste0(
  "Overall effect: ",
  "z = ", round(abs_zp_overall_6m$z_value, 2),
  ", p = ", formatC(abs_zp_overall_6m$p_value, digits = 2),
  ", NNT = ", abs_zp_overall_6m$NNT
)

# Adjust the footer for the subgroup effects after implicit subgroup
grid.text(footer_imp_abs_6m, x = 0.094, y = 0.470,
          just = "left", gp = gpar(fontsize = 10))

# Adjust the footer for the subgroup effects after explicit subgroup
grid.text(footer_exp_abs_6m, x = 0.094, y = 0.230,
          just = "left", gp = gpar(fontsize = 10))

# Adjust the footer for the overall effect to the bottom left
grid.text(footer_over_abs_6m, x = 0.094, y = 0.060,
          just = "left", gp = gpar(fontsize = 10))
```

If we want to know the prediction intervals without outputting it to the plot, we can print them separately.

```{r abs-6m-pi, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Displaying the log-transformed prediction interval (PI) from the metagen output and rounding the output
round(
  exp(cbind(
    LL = abs_metagen_6m$lower.predict.w,
    UL = abs_metagen_6m$upper.predict.w
    )
  ), 5
)
```

### 3.1.3 Publication bias for intermediate effects on abstinence

To assess for potential publication bias , we need to create a funnel plot for the studies assessing the intermediate effects.
Before the funnel plot can be created, we will be changing the author names to fit the APA-format using the previously defined study labels.

```{r abs-6m-pub-labels}
# Assign the new study labels to the data frame
abs_d_full_6m$study <- ifelse(abs_d_full_6m$study %in% names(study_labels),
                            study_labels[abs_d_full_6m$study],
                            abs_d_full_6m$study)
```

After defining the new labels, we can run a separate meta-analysis on the intermediate time point.

```{r abs-6m-pub-metagen, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Run the meta-analysis stratified by cognitive systems and using the new labels
abs_metagen_6m <- metagen(TE = lnOR,
                    seTE = SElnOR,
                    studlab = study,
                    data = abs_d_full_6m,
                    sm = "OR",
                    method.tau = "REML",
                    common = FALSE,
                    random = TRUE)
```

Now we can run an Egger's test, but due to a low number of studies, we need to set the minimum *k* to four studies.
The results will, however, be less reliable given the small number of studies, and interpretation of the results should be cautioned.

```{r abs-6m-eggers-test, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Conduct an Egger's test using the previously calculated treatment effects
abs_egger_6m <- metabias(abs_metagen_6m, method.bias = "Egger", k.min = 4)

# Print the results of the Egger's test
print(abs_egger_6m)
```

Now with the results from the Egger's test, we can now create the funnel plot using the meta-package inbuilt function funnel().
We can add the test statistic from the Egger's test to the funnel plot using mtext().
As there is a high variability among these studies, we will need to adjust the limits of the x-axis so the studies can be better displayed.

```{r abs-6m-funnel-plot, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Funnel plot for studies with intermediate-term effects on abstinence"}
# Create a funnel plot with adjusted x-axis
funnel(abs_metagen_6m,
       xlab = "Odds ratio",
       studlab = TRUE,
       pch = 17,
       cex = 1)

# Add Egger's test statistic to the plot
abs_egger_text_6m <- paste0("Egger's test: p = ", 
                     round(abs_egger_6m$p.value, 3))

# Define the actual placement of the statistics on the funnel plot
mtext(abs_egger_text_6m, side=3, line=0.5, adj=0, cex=0.9, col="black")
```

## 3.2 Intermediate-term alcohol reduction

The second part of our analyses will be conducted on our secondary outcome of alcohol reduction, and we calculate the effect sizes for the intermediate-term time point.

### 3.2.1 Calculation of effect sizes for intermediate-term continuous variables

We want to follow the procedure of as above and filter the data by the time point "6 months".

```{r red-6m-filter, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Filter 6 month data first and store it as a new subset
red_d_6m <- red_d %>% filter(time_point == "6 months")
```

As we only have continuous data for alcohol reduction, we only need to run the metacont() on our dataset to calculate the SMDs using Hedge's *g* correction.

```{r red-6m-metacont, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Calculating the SMDs (Hedge's g) using metacont()
red_metacont_6m <- metacont(
  n.e = e_n,
  mean.e = e_reduc_mean,
  sd.e = e_reduc_sd,
  n.c = c_n,
  mean.c = c_reduc_mean,
  sd.c = c_reduc_sd,
  studlab = study,
  data = red_d_6m,
  sm = "SMD",
  method.smd = "Hedges",
  method.tau = "REML",
  method.random.ci = "classic",
  random = TRUE
)
```

Now we can combine the calculated effect sizes and add them to the original data set without changing the original variable names.

```{r red-6m-combined, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Combine the SMDs calculated with original variables and store it in a new data frame
red_d_full_6m <- data.frame(
  row_id = red_d_6m$row_id,
  study = red_metacont_6m$studlab,
  time_point = red_d_6m$time_point,
  system = red_d_6m$system,
  intervention = red_d_6m$intervention,
  total_n = red_d_6m$e_n + red_d_6m$c_n, # Calculating total number of participants
  c_n = red_d_6m$c_n,
  c_reduc_mean = red_d_6m$c_reduc_mean,
  c_reduc_sd = red_d_6m$c_reduc_sd,
  e_n = red_d_6m$e_n,
  e_reduc_mean = red_d_6m$e_reduc_mean,
  e_reduc_sd = red_d_6m$e_reduc_sd,
  # Adding calculated SMDs to the data frame 
  SMD = red_metacont_6m$TE,
  SE = red_metacont_6m$seTE,
  LCI = red_metacont_6m$lower,
  UCI = red_metacont_6m$upper,
  # Adding the z- and p-values
  `z-value` = red_metacont_6m$TE / red_metacont_6m$seTE,
  `p-value` = 2 * (1 - pnorm(abs(red_metacont_6m$TE / red_metacont_6m$seTE))),
  # Adding a final note on how data was converted    
  Notes = "Calculated using metacont()",
  check.names = FALSE # Removing the period as a space
)
```

To use the same author labels in APA-format across all studies and sub-studies, we need to apply the previously defined study labels to our integrated data set.

```{r red-6m-assign-labels}
# Assign the new study labels to the combined data frame
red_d_full_6m$study <- ifelse(red_d_full_6m$study %in% names(study_labels),
                            study_labels[red_d_full_6m$study],
                            red_d_full_6m$study)
```

We want to have the author labels sorted alphabetically rather than in accordance with the pre-specified study IDs and row numbers, so we first arrange the list of studies.

```{r red-6m-arrange-alpha, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Arrange studies alphabetically
red_d_full_6m <- red_d_full_6m %>%
  arrange(study)
```

\### 3.2.2 Meta-analysis of intermediate-term effects on alcohol reduction

Now with the newly defined subgroup labels, we can conduct the meta-analysis using metagen().

```{r red-6m-metagen, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Run the meta-analysis stratified by cognitive systems and using the new labels
red_metagen_6m <- metagen(TE = SMD,
                    seTE = SE,
                    studlab = study,
                    data = red_d_full_6m,
                    sm = "SMD",
                    method.tau = "REML",
                    common = FALSE,
                    random = TRUE,
                    method.random.ci = "classic")

# Print the results of the meta-analysis
print(red_metagen_6m)
```

Now that we have created a list for the test statistics for each of the time points, we can create the final forest plot.

```{r red-6m-forest, fig.height=5, fig.width=12, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Forest plot of intermediate-term effects on alcohol reduction"}
# Now plot the forest plot again with new subgroup names
forest(red_metagen_6m,
       prediction = TRUE,
       layout = "BMJ",
       overall = TRUE,
       random = TRUE,
       common = FALSE,
       test.subgroup = FALSE,
       print.stat = FALSE,
       print.I2 = TRUE,
       print.Q = TRUE,
       print.pval.Q = TRUE,
       print.tau2 = FALSE,
       label.left = "Favors Control",
       label.right = "Favors Intervention",
       spacing = 1.2,
       fontsize = 10,
       digits = 2,
       leftcols = c("studlab", "e_n", "e_reduc_mean", "e_reduc_sd", "c_n", "c_reduc_mean",
                    "c_reduc_sd"),
       leftlabs = c("Study", "Intv. (n)", "Mean", "SD", 
                    "Ctrl. (n)", "Mean", "SD"),
       just.addcols = "center"
       )

```

### 3.2.3 Publication bias for intermediate effects on alcohol reduction

Though an Egger's test will not have the required statistical power, any interpretation of the results should be highly cautioned.
However, we proceed with conducting the test and adding it to the final plot.

```{r red-6m-eggers-test, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Conduct an Egger's test using the previously calculated treatment effects
red_egger_6m <- metabias(red_metagen_6m, method.bias = "Egger", k.min = 2)
```

We can now create the funnel plot and add the result of the Egger's test.

```{r red-6m-funnel-plot, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Funnel plot of studies with intermediate-term effects on alcohol reduction"}
# Create a funnel plot for the 6 month time point
funnel(red_metagen_6m,
       xlab = "Standardised Mean Difference",
       studlab = TRUE,
       pch = 17,
       cex = 0.5)

# Add Egger's test statistic to the plot
red_egger_text_6m <- paste0("Egger's test: p = ", 
                     round(red_egger_6m$p.value, 3))

# Define the actual placement of the statistics on the funnel plot
mtext(red_egger_text_6m, side=3, line=0.5, adj=0, cex=0.9, col="black")
```

## 3.3 Intermediate-term craving

The second part of our analyses will be conducted on our secondary outcome of craving, and we calculate the effect sizes for the intermediate-term time point.

### 3.3.1 Calculation of effect sizes for intermediate-term continuous variables

We want to follow the procedure of as above and filter the data by the time point "6 months".

```{r crav-6m-filter, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Filter 6 month data first and store it as a new subset
crav_d_6m <- crav_d %>% filter(time_point == "6 months")
```

As we only have continuous data for alcohol reduction, we only need to run the metacont() on our dataset to calculate the SMDs using Hedge's *g* correction.

```{r crav-6m-metacont, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Calculating the SMDs (Hedge's g) using metacont()
crav_metacont_6m <- metacont(
  n.e = e_n,
  mean.e = e_crav_mean,
  sd.e = e_crav_sd,
  n.c = c_n,
  mean.c = c_crav_mean,
  sd.c = c_crav_sd,
  studlab = study,
  data = crav_d_6m,
  sm = "SMD",
  method.smd = "Hedges",
  method.tau = "REML",
  method.random.ci = "classic",
  random = TRUE
)
```

Now we can combine the calculated effect sizes and add them to the original data set without changing the original variable names.

```{r crav-6m-combined, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Combine the SMDs calculated with original variables and store it in a new data frame
crav_d_full_6m <- data.frame(
  row_id = crav_d_6m$row_id,
  study = crav_metacont_6m$studlab,
  time_point = crav_d_6m$time_point,
  system = crav_d_6m$system,
  intervention = crav_d_6m$intervention,
  total_n = crav_d_6m$e_n + crav_d_6m$c_n, # Calculating total number of participants
  c_n = crav_d_6m$c_n,
  c_crav_mean = crav_d_6m$c_crav_mean,
  c_crav_sd = crav_d_6m$c_crav_sd,
  e_n = crav_d_6m$e_n,
  e_crav_mean = crav_d_6m$e_crav_mean,
  e_crav_sd = crav_d_6m$e_crav_sd,
  # Adding calculated SMDs to the data frame 
  SMD = crav_metacont_6m$TE,
  SE = crav_metacont_6m$seTE,
  LCI = crav_metacont_6m$lower,
  UCI = crav_metacont_6m$upper,
  # Adding the z- and p-values
  `z-value` = crav_metacont_6m$TE / crav_metacont_6m$seTE,
  `p-value` = 2 * (1 - pnorm(abs(crav_metacont_6m$TE / crav_metacont_6m$seTE))),
  # Adding a final note on how data was converted    
  Notes = "Calculated using metacont()",
  check.names = FALSE # Removing the period as a space
)
```

To use the same author labels in APA-format across all studies and sub-studies, we need to apply the previously defined study labels to our integrated data set.

```{r crav-6m-assign-labels}
# Assign the new study labels to the combined data frame
crav_d_full_6m$study <- ifelse(crav_d_full_6m$study %in% names(study_labels),
                            study_labels[crav_d_full_6m$study],
                            crav_d_full_6m$study)
```

We want to have the author labels sorted alphabetically rather than in accordance with the pre-specified study IDs and row numbers, so we first arrange the list of studies.

```{r crav-6m-arrange-alpha, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Arrange studies alphabetically
crav_d_full_6m <- crav_d_full_6m %>%
  arrange(study)
```

### 3.2.2 Meta-analysis of intermediate-term effects on alcohol reduction

Now with the newly defined subgroup labels, we can conduct the meta-analysis using metagen(), but this time set the parameter for subgroups to the label "Time point" and use the classic *z*-test for the random effects model.

```{r crav-6m-metagen, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Run the meta-analysis stratified by cognitive systems and using the new labels
crav_metagen_6m <- metagen(TE = SMD,
                    seTE = SE,
                    studlab = study,
                    data = crav_d_full_6m,
                    sm = "SMD",
                    method.tau = "REML",
                    common = FALSE,
                    random = TRUE,
                    method.random.ci = "classic")

# Print the results of the meta-analysis
print(crav_metagen_6m)
```

Now that we have created a list for the test statistics for each of the time points, we can create the final forest plot.

```{r crav-6m-forest, fig.height=6, fig.width=11, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Forest plot of intermediate-term effects on craving"}
# Now plot the forest plot again with new subgroup names
forest(crav_metagen_6m,
       prediction = TRUE,
       layout = "BMJ",
       overall = TRUE,
       random = TRUE,
       common = FALSE,
       test.subgroup = FALSE,
       print.stat = FALSE,
       print.I2 = TRUE,
       print.Q = TRUE,
       print.pval.Q = TRUE,
       print.tau2 = FALSE,
       label.left = "Favors Control",
       label.right = "Favors Intervention",
       spacing = 1.2,
       fontsize = 10,
       digits = 2,
       leftcols = c("studlab", "e_n", "e_crav_mean", "e_crav_sd", "c_n", "c_crav_mean",
                    "c_crav_sd"),
       leftlabs = c("Study", "Intv. (n)", "Mean", "SD", 
                    "Ctrl. (n)", "Mean", "SD"),
       just.addcols = "center"
       )

```

### 3.2.3 Publication bias for intermediate effects on alcohol reduction

As we only identified two studies for the intermediate-term effects on craving, a visual inspection for asymmetry will not be meaningful nor will there be sufficient power for an Egger's test.

