# 4. Main analyses on long-term outcomes

The third and last part of the main analyses will be conducted on long-term effects on outcomes 12 months after discharge.
We still use the excel-dataset "Extracted Clinical Outcome Data", but this time we will only be filtering the data sheets by time point for the calculation of effect sizes and not when conducting the meta-analyses

## 4.1 Long-term abstinence

First we conduct the analyses on our primary outcome of abstinence, and we calculate the effect sizes for the long-term time point.

### 4.1.1 Calculation of effect sizes for long-term continuous variables

We can now apply the above methodology for our time point of 12 months, which requires us first to filter the data set.

```{r abs-12m-filter, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Filter 12 month data first and store it as a new subset
abs_d_12m <- abs_d %>% filter(time_point == "12 months")
```

The calculation of effect sizes will be done by the inbuilt functions in the meta-package, so for the categorical variables, we will use the metabin() function.

```{r abs-12m-metabin, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Calculating the lnORs using metabin()
abs_metabin_12m <- metabin(
  event.e = e_abs,
  n.e = e_n,
  event.c = c_abs,
  n.c = c_n,
  studlab = study,
  data = abs_d_12m,
  sm = "OR",
  method.tau = "REML",
  method.random.ci = "classic",
  random = TRUE,
  incr = 0.5,
  allstudies = TRUE
)
```

After we have calculated the lnORs, we can create a new data frame and store these values alongside with the other relevant variables (e.g., time point, number of abstinents, etc.) from our original dataset.
As performed previously, we calculate the ORs and SMDs using the Chinn-factor.
Finally, we add the z- and p-values to the data-frame.

```{r abs-12m-combined-data, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Fetching the previously stored data frame and adding the lnORs, their SE and 95% CI
abs_d_full_12m <- data.frame(
  row_id = abs_d_12m$row_id,
  study = abs_metabin_12m$studlab,
  time_point = abs_d_12m$time_point,
  system = abs_d_12m$system,
  intervention = abs_d_12m$intervention,
  total_n = abs_d_12m$e_n + abs_d_12m$c_n,
  c_n = abs_d_12m$c_n,
  c_abs = abs_d_12m$c_abs,
  c_non_abs = abs_d_12m$c_n - abs_d_12m$c_abs,
  e_n = abs_d_12m$e_n,
  e_abs = abs_d_12m$e_abs,
  e_non_abs = abs_d_12m$e_n - abs_d_12m$e_abs,
# Extracting the lnORs from the metabin results
  lnOR = abs_metabin_12m$TE,
  SElnOR = abs_metabin_12m$seTE,
  lnLCI = abs_metabin_12m$lower,
  lnUCI = abs_metabin_12m$upper,
# Calculating the ORs from the metabin results
  OR = exp(abs_metabin_12m$TE),
  OrSE = exp(abs_metabin_12m$TE) * abs_metabin_12m$seTE,
  OrLCI = exp(abs_metabin_12m$lower),
  OrUCI = exp(abs_metabin_12m$upper),
# Calculating the SMD, SE and 95% CI using the Chinn-function
  SMD = abs_metabin_12m$TE * chinn_lnor_to_smd,
  SE = abs_metabin_12m$seTE * chinn_lnor_to_smd,
  LCI = abs_metabin_12m$lower * chinn_lnor_to_smd,
  UCI = abs_metabin_12m$upper * chinn_lnor_to_smd,
# Adding the z- and p-values
  `z-value` = abs_metabin_12m$TE / abs_metabin_12m$seTE,
  `p-value` = 2 * (1 - pnorm(abs(abs_metabin_12m$TE / abs_metabin_12m$seTE))),
# Adding a final note on how data was converted    
  Notes = "Continuous variables converted from categorical outcome (metabin) using Chinn's formula",
  check.names = FALSE
)
```

We can rename the subgroups for later use for data export.

```{r abs-12m-rename-subgroups, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Assigning new variable names to the subgroups
abs_d_full_12m <- abs_d_full_12m %>%
  dplyr::rename(`Cognitive system` = system) %>%
  dplyr::mutate( # Changing the order of the two subgroups
    `Cognitive system` = factor(`Cognitive system`,
                      levels = c("Implicit", "Explicit"))
    )
```

First we need to assign study labels to the data frame for 12 months.

```{r abs-12m-assign-labels}
# Assign the new study labels to the combined data frame
abs_d_full_12m <- abs_d_full_12m %>%
  mutate(
    study = ifelse(
      study %in% names(study_labels),
      study_labels[study],
      study
    )
  )
```

We want to have the author labels sorted alphabetically rather than in accordance with the pre-specified study IDs and row numbers, so we first arrange the list of studies.

```{r abs-12m-arrange-alpha, echo=TRUE, message=FALSE,}
# Arrange studies alphabetically
abs_d_full_12m <- abs_d_full_12m %>%
  arrange(study)
```

We can now calculate the baseline control risk for the long-term effects by only including studies with categorical outcomes.

```{r abs-12m-ctrl-abs-rate, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Abstinence rate risk difference across all studies on short-term effects
p_c_abs_12m <- with(abs_d_full_12m, sum(c_abs) / sum(c_n))
```

### 4.1.2 Meta-analysis of long-term effects on abstinence

Now with the newly defined subgroup labels, we can conduct the meta-analysis using metagen().

```{r abs-12m-metagen, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Run the meta-analysis stratified by cognitive systems and using the new labels
abs_metagen_12m <- metagen(TE = lnOR,
                    seTE = SElnOR,
                    studlab = study,
                    data = abs_d_full_12m,
                    sm = "OR",
                    method.tau = "REML",
                    common = FALSE,
                    random = TRUE,
                    method.random.ci = "classic")

# Print the results of the meta-analysis
print(abs_metagen_12m)
```

It is now possible to extract the test statistics for the individual time points, which can be used for the forest plot.

```{r abs-12m-zp-values, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Extract the test statistics for the subgroup analysis and create a data frame
abs_zp_overall_12m <- data.frame(
  lnOR = abs_metagen_12m$TE.random,
  lnOR_se = abs_metagen_12m$seTE.random,
  NNT = round(nnt(exp(abs_metagen_12m$TE.random), p_c_abs_12m)),
  z_value = abs_metagen_12m$statistic.random,
  p_value = abs_metagen_12m$pval.random
)

# Extract the test statistics for the subgroup analysis and create a data frame
abs_zp_subgroup_12m <- data.frame(
  subgroup = abs_metagen_12m$bylevs,
  lnOR = abs_metagen_12m$TE.random.w,
  lnOR_se = abs_metagen_12m$seTE.random.w,
  NNT = round(nnt(abs_metagen_12m$TE.random.w, p_c_abs_12m)),
  z_value = abs_metagen_12m$statistic.random.w,
  p_value = abs_metagen_12m$pval.random.w
)
```

Now that we have created a list for the test statistics for each of the time points, we can create the final forest plot.

```{r abs-12m-forest, fig.height=5, fig.width=10, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Forest plot for the long-term effects on abstinence"}
# Now plot the forest plot again with new subgroup names
forest(abs_metagen_12m,
       prediction = TRUE,
       layout = "BMJ",
       overall = TRUE,
       random = TRUE,
       common = FALSE,
       test.subgroup = FALSE,
       print.stat = FALSE,
       print.I2 = TRUE,
       print.Q = TRUE,
       print.pval.Q = TRUE,
       print.tau2 = FALSE,
       label.left = "Favors Control",
       label.right = "Favors Intervention",
       spacing = 1.2,
       fontsize = 10,
       digits = 2,
       xlim = c(1/15, 15),
       at = c(0.07, 0.2, 0.5, 1, 2, 5, 15),
       leftcols = c("studlab", "e_abs", "e_n", "c_abs", "c_n"),
       leftlabs = c("Study", "Intv. (events)", "Total (n)", "Ctrl. (events)", "Total (n)"),
       rightcols = c("w.random", "effect", "ci"),
       rightlabs = c("Weight (%)", "OR", "95% CI")
       )

footer_over_abs_12m <- paste0(
  "Overall effect: ",
  "z = ", round(abs_zp_overall_12m$z_value, 2),
  ", p = ", formatC(abs_zp_overall_12m$p_value, digits = 2),
  ", NNT = ", abs_zp_overall_12m$NNT
)

# Adjust the footer for the overall effect to the bottom left
grid.text(footer_over_abs_12m, x = 0.017, y = 0.06,
          just = "left", gp = gpar(fontsize = 10))
```

### 4.1.3 Publication bias for long-term effects on abstinence

Now we can run an Egger's test, but due to a low number of studies, we need to set the minimum *k* to eight studies.
The results will, however, be less reliable given the small number of studies, and interpretation of the results should be cautioned.

```{r abs-12m-eggers-test, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Conduct an Egger's test using the previously calculated treatment effects
abs_egger_12m <- metabias(abs_metagen_12m, method.bias = "Egger", k.min = 8)

# Print the results of the Egger's test
print(abs_egger_12m)
```

Now with the results from the Egger's test, we can now create the funnel plot using the meta-package inbuilt function funnel().
We can add the test statistic from the Egger's test to the funnel plot using mtext().
As there is a high variability among these studies, we will need to adjust the limits of the x-axis so the studies can be better displayed.

```{r abs-12m-funnel-plot, fig.height=8, fig.width=8, message=FALSE, warning=FALSE, include=TRUE, fig.cap="Funnel plot of studies with long-term effects on abstinence"}
# Create a funnel plot for the 12 month time point
funnel(abs_metagen_12m,
       xlab = "Odds Ratio",
       studlab = TRUE,
       pch = 17,
       cex = 0.5)

# Add Egger's test statistic to the plot
abs_egger_text_12m <- paste0("Egger's test: p = ", 
                     round(abs_egger_12m$p.value, 3))

# Define the actual placement of the statistics on the funnel plot
mtext(abs_egger_text_12m, side=3, line=0.5, adj=0, cex=0.9, col="black")
```

## 4.2 Long-term effects on alcohol reduction

### 4.2.1 Calculation of effect sizes for long-term continuous variables

We repeat the procedure as in the above section but this time filter the data by the time point "12 months".

```{r red-12m-filter, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Filter 6 month data first and store it as a new subset
red_d_12m <- red_d %>% filter(time_point == "12 months")
```

As we only have continuous data for alcohol reduction, we only need to run the metacont() on our dataset to calculate the SMDs using Hedge's *g* correction.

```{r red-12m-metacont, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Calculating the SMDs (Hedge's g) using metacont()
red_metacont_12m <- metacont(
  n.e = e_n,
  mean.e = e_reduc_mean,
  sd.e = e_reduc_sd,
  n.c = c_n,
  mean.c = c_reduc_mean,
  sd.c = c_reduc_sd,
  studlab = study,
  data = red_d_12m,
  sm = "SMD",
  method.smd = "Hedges",
  method.tau = "REML",
  method.random.ci = "classic",
  random = TRUE
)
```

Now we can combine the calculated effect sizes and add them to the original data set without changing the original variable names.

```{r red-12m-combined, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Combine the SMDs calculated with original variables and store it in a new data frame
red_d_full_12m <- data.frame(
  row_id = red_d_12m$row_id,
  study = red_metacont_12m$studlab,
  time_point = red_d_12m$time_point,
  system = red_d_12m$system,
  intervention = red_d_12m$intervention,
  total_n = red_d_12m$e_n + red_d_12m$c_n, # Calculating total number of participants
  c_n = red_d_12m$c_n,
  c_reduc_mean = red_d_12m$c_reduc_mean,
  c_reduc_sd = red_d_12m$c_reduc_sd,
  e_n = red_d_12m$e_n,
  e_reduc_mean = red_d_12m$e_reduc_mean,
  e_reduc_sd = red_d_12m$e_reduc_sd,
  # Adding calculated SMDs to the data frame 
  SMD = red_metacont_12m$TE,
  SE = red_metacont_12m$seTE,
  LCI = red_metacont_12m$lower,
  UCI = red_metacont_12m$upper,
  # Adding the z- and p-values
  `z-value` = red_metacont_12m$TE / red_metacont_12m$seTE,
  `p-value` = 2 * (1 - pnorm(abs(red_metacont_12m$TE / red_metacont_12m$seTE))),
  # Adding a final note on how data was converted    
  Notes = "Calculated using metacont()",
  check.names = FALSE # Removing the period as a space
)
```

### 4.2.2 Meta-analysis of long-term effects on alcohol reduction

As we only identified one study examining long-term effects on alcohol reduction, a meta-analysis could not be performed.

### 4.2.3 Publication bias for long-term effects on alcohol reduction

An assessment of publication bias was not possible due to insufficient studies.

## 4.3 Long-term effects on craving

The last part of our main analyses will be conducted on alcohol craving, and we calculate the effect sizes for the long-term time point.

### 4.3.1 Calculation of effect sizes for long-term continuous variables

We repeat the methodology used previously and start with filtering the data for 12 months

```{r crav-12m-filter, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Filter 6 month data first and store it as a new subset
crav_d_12m <- crav_d %>% filter(time_point == "12 months")
```

As we only have continuous data for alcohol craving, we only need to run the metacont()-function on our dataset to calculate the SMDs using Hedge's *g* correction.

```{r crav-12m-metacont, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Calculating the SMDs (Hedge's g) using metacont()
crav_metacont_12m <- metacont(
  n.e = e_n,
  mean.e = e_crav_mean,
  sd.e = e_crav_sd,
  n.c = c_n,
  mean.c = c_crav_mean,
  sd.c = c_crav_sd,
  studlab = study,
  data = crav_d_12m,
  sm = "SMD",
  method.smd = "Hedges",
  method.tau = "REML",
  method.random.ci = "classic",
  random = TRUE
)
```

Now we can combine the calculated effect sizes and add them to the original data set without changing the original variable names.

```{r crav-12m-combined, echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
# Combine the SMDs calculated with original variables and store it in a new data frame
crav_d_full_12m <- data.frame(
  row_id = crav_d_12m$row_id,
  study = crav_metacont_12m$studlab,
  time_point = crav_d_12m$time_point,
  system = crav_d_12m$system,
  intervention = crav_d_12m$intervention,
  total_n = crav_d_12m$e_n + crav_d_12m$c_n, # Calculating total number of participants
  c_n = crav_d_12m$c_n,
  c_crav_mean = crav_d_12m$c_crav_mean,
  c_crav_sd = crav_d_12m$c_crav_sd,
  e_n = crav_d_12m$e_n,
  e_crav_mean = crav_d_12m$e_crav_mean,
  e_crav_sd = crav_d_12m$e_crav_sd,
  # Adding calculated SMDs to the data frame 
  SMD = crav_metacont_12m$TE,
  SE = crav_metacont_12m$seTE,
  LCI = crav_metacont_12m$lower,
  UCI = crav_metacont_12m$upper,
  # Adding the z- and p-values
  `z-value` = crav_metacont_12m$TE / crav_metacont_12m$seTE,
  `p-value` = 2 * (1 - pnorm(abs(crav_metacont_12m$TE / crav_metacont_12m$seTE))),
  # Adding a final note on how data was converted    
  Notes = "Calculated using metacont()",
  check.names = FALSE # Removing the period as a space
)
```

### 4.3.2 Meta-analysis of long-term effects on craving

As only one study was identified on long-term effects on craving, no meta-analysis could be performed.

### 4.3.3 Publication bias for intermediate effects on craving

An assessment of publication bias was not possible due to insufficient studies.

